Improving phase-matching of FWM with temperature

### 2015-09-21 latex/article.tex
nefastità

\usepackage{caption}		% to use subfigure
\usepackage{subcaption}

@@

@@

\subsection{Data analysis}

@@

We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
We observed the presence of different (mainly one or two) peaks in wavelength which were almost conserved in the temperature shift.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=.75\textwidth]{ex_pos.png}
	\caption{Example of peaks vs $T_H$.}
	\label{fig_example_position}
\end{figure}
\begin{figure}[!h]
	\centering
%	\includegraphics[scale=1]{ex_bw.png}
	\includegraphics[width=.75\textwidth]{ex_bw.png}
	\caption{Example of bandwidth vs $T_H$.}
	\label{fig_example_bandwidth}
\end{figure}

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.45\textwidth}
%		\includegraphics[width=1\textwidth]{ex_pos.png}
%		\caption{Example of peaks vs $T_H$.}
%		\label{fig_example_position}
%	\end{subfigure}%\hspace{.02\textwidth}
%	\begin{subfigure}[b]{0.45\textwidth}
%		\includegraphics[width=1\textwidth]{ex_bw.png}
%		\caption{Example of bandwidth vs $T_H$.}
%		\label{fig_example_bandwidth}
%	\end{subfigure}
%	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
%	\label{fig_examples}
%\end{figure}

\section{Results}
\subsubsection{data aggregation}
Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected there were one or two straight lines.
Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.

%The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{ppaat2.png}
		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
								% 2 = no points at 1.55um
		\caption{Peaks position at $T_{amb}$.}
	\end{subfigure}
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{ppc2.png}
		\label{fig_sym_ppc2} % ppc = bandwidth change
		\caption{Change of peak position.}
	\end{subfigure}
	\caption{Peak position summary}
	\label{fig_sym_pp}
\end{figure}

>>>>

\usepackage{caption}		% to use subfigure
\usepackage{subcaption}
\usepackage{sidecap}

@@

\begin{equation}
	\Delta k = 2\beta_P(\omega_P)-\beta_S(\omega_S)-\beta_I(2\omega_P-\omega_S)
\end{equation}

@@

@@

\subsection{Data analysis}
We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
We observed the presence of different (mainly one or two) peaks in wavelength which were almost conserved in the temperature shift.

@@

\begin{SCfigure}%[!h]
	\centering
	\includegraphics[width=.64\textwidth]{ex_pos.png}
	\caption{Example of peak position vs $T_H$.}
	\label{fig_example_position}
\end{SCfigure}
\begin{SCfigure}%[!h]
	\centering
%	\includegraphics[scale=1]{ex_bw.png}
	\includegraphics[width=.64\textwidth]{ex_bw.png}
	\caption{Example of bandwidth vs $T_H$.}
	\label{fig_example_bandwidth}
\end{SCfigure}

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.49\textwidth}
%		\includegraphics[width=1\textwidth]{ex_pos.png}
%		\caption{Example of peaks vs $T_H$.}
%		\label{fig_example_position}
%	\end{subfigure}%\hspace{.02\textwidth}
%	\begin{subfigure}[b]{0.49\textwidth}
%		\includegraphics[width=1\textwidth]{ex_bw.png}
%		\caption{Example of bandwidth vs $T_H$.}
%		\label{fig_example_bandwidth}
%	\end{subfigure}
%	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
%	\label{fig_examples}
%\end{figure}

\section{Results}
\subsubsection{data aggregation}
Examining the graphs obtained from the data analysis of the symmetric configuration, we noticed that for each solution selected there were one or two straight lines.
Therefore we summarized them by collecting the slopes and the value of the functions at ambient temperature.
To make the graphs easier to read, we excluded set of data the pointsof no interest: those which peak had the same frequency $\omega_P = \SI{1.55}{\um}$ of the pump.

The first Figure (\ref{fig_sym_pp@t2}) tell us where we found phase-matching condition.
We can see that every set has its symmetric one.
For example, combination \texttt{517} is the symmetric of \texttt{571}.
In the coupled equations and in the 
%The next Figures (\ref{fig_sym_pp}) and (\ref{fig_sym_bw}) show the results obtained, excluding the sets which only phasematch was at $\lambda = \SI{1.55}{\um}$

\begin{figure}[!h]
	\centering
	\includegraphics[width=.75\textwidth]{ppaat2.png}
	\caption{Peak position at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler orders.}
	\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb, 2 = no points at 1.55um
\end{figure}

\begin{figure}[!h]
	\centering
	\includegraphics[width=.75\textwidth]{ppc2.png}
	\caption{Change of peak position.}
	\label{fig_sym_ppc2} % ppc = bandwidth change
\end{figure}
